---
title: "R Notebook"
output: html_notebook
---

```{r}
library(data.table)
library(tidyverse)
library(cowplot)
```



Download all our Data for chromosome 1
```{r}
allpops_Chrom1<-fread("~/Desktop/All_pop_1Kb_filt.csv") %>% select(CHROM,BIN_START,BIN_END,PI,NBR_BP,pop,N_VARIANTS) %>% filter(CHROM==1)
```

get genetic map from Ogut 2015 for chromosome1; correct so minimum is 0
```{r}
gen_map<-fread("~/Desktop/ogut_fifthcM_map_agpv4_INCLUDE.txt") %>%
   rename(name=V1, marker=V2, chrom=V4, pos=V5, cm=V3) %>% 
  filter(chrom==1) %>% mutate(cm=cm+abs(min(cm)))
```

Get positon of Genes, RNA, EXONS,CDS five_prime_UTR from Zea_mays.B73_RefGen_v4.44.chromosome.1.gff3
```{r}
read.delim("~/Downloads/Zea_mays.B73_RefGen_v4.44.chromosome.1.gff3", header=F, comment.char="#") -> gff
 
```

Filtering data so we only get data for genes, removing columns
```{r}
Gene_position<-filter(gff, V3=="gene")  %>%
  select(-V8, -V6, -V9)  

```

let’s get cm positions for genes in each pop; remove genes with NA (usually because before start of genetic map)
```{r}
teo_CM_gene1<-mutate(Gene_position,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=Gene_position$V4)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=Gene_position$V5)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")
```

Cleaning up data, removing columns, renaming certain columns so they can be read by bedtools, convernting CM to integers by multiplying 1000000000 and removing decimal places (Bedtools only reads integers)
```{r}
TEO_CM_GENE_CHROM_1<-teo_CM_gene1 %>% select(-V2,-V3,-V4,-V5,-V7,-rec) %>% mutate(cm_start=cm_start*1000000000, cm_end=cm_end*1000000000) %>% mutate (cm_start=round(cm_start, digits=0), cm_end=round(cm_end, digits=0)) %>% rename(chrom=V1, chromStart=cm_start, chromEnd=cm_end) 

TEO_CM_GENE_CHROM_1$chrom<-"chr1" 
```

Get any possible Window positions from any Teosinte population Chrom 1 and rearragning them in the order that bedtools can read 
```{r}
TEOWindows <- data.frame(BIN_START=seq(33001,306878001,1000),
                 BIN_END=seq(34000,306879000,1000),
                 chrom="chr1")
                 
TEOWindows<-TEOWindows[c("chrom", "BIN_START", "BIN_END")]

```

Get cm positions for windows in each pop; remove windows with NA (usually because before start of genetic map)
```{r}
TEOWindows<-mutate(TEOWindows,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=TEOWindows$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=TEOWindows$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")
```

Cleaning up data, removing columns, renaming certain columns so they can be read by bedtools, converting CM to integers by multiplying 1000000000 and removing decimal places
```{r}
TEO_All_POPS_CM_WINDOW_CHROM_1<-TEOWindows %>% select(-BIN_START, -BIN_END,  -rec) %>% mutate(cm_start=cm_start*1000000000, cm_end=cm_end*1000000000) %>% mutate (cm_start=round(cm_start, digits=0), cm_end=round(cm_end, digits=0)) %>% rename( chromStart=cm_start, chromEnd=cm_end)
```


No e in my textfiles...Eliminating scientific notation
```{r}
options(scipen = 999)
```

Make Textfiles for Bedtools
```{r}
write.table(TEO_CM_GENE_CHROM_1, file="TEO_CM_GENE_CHROM_1.txt",row.names=F,quote=F,sep="\t")
write.table(TEO_All_POPS_CM_WINDOW_CHROM_1, file="TEO_All_POPS_CM_WINDOW_CHROM_1.txt",row.names=F,quote=F,sep="\t")
```

Read Bedtools distance file
```{r}
read.delim("~/Documents/All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt", header=F, comment.char="#")-> All_TEO_Distance_Between_1000BPWindow_and_Gene_CM.txt  
```

Renaming Column names for TEOBedtools file
```{r}
All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt<-All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt %>% rename(chromWindow=V1, cm_start=V2, cm_end=V3, chromGene=V4, GeneCM_Start=V5, GeneCM_End=V6, Distance=V7 )
```

Converting integer CM back into CM (Bedtools only reads integers)
```{r}
All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt<-All_TEO_Distance_Between_1000BPWindow_and_Gene_CM.txt %>% mutate(cm_start=cm_start/1000000000,cm_end=cm_end/1000000000,GeneCM_Start=GeneCM_Start/1000000000,GeneCM_End=GeneCM_End/1000000000, Distance=Distance/1000000000 ) 
```  

Lets get data for our Teosinte populations
```{r}
teo_palmar_Chrom1<-filter(allpops_Chrom1,pop=="Teo_Palmar_Chico")
teo_sanlo_Chrom1<-filter(allpops_Chrom1,pop=="Teo_San_Lorenzo")
teo_amatlan_Chrom1<-filter(allpops_Chrom1,pop=="Teo_Amatlan_de_Canas")
teo_elrodeo_Chrom1<-filter(allpops_Chrom1,pop=="Teo_El_Rodeo")
teo_cruc_Chrom1<-filter(allpops_Chrom1,pop=="Teo_Crucero_Lagunitas")
teo_losguajes_Chrom1<-filter(allpops_Chrom1,pop=="Teo_Los_Guajes")
```


Lets get CM positions for our Windows in our Teosinte data
```{r}
teo_palmar_Chrom1<-mutate(teo_palmar_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_palmar_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_palmar_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

teo_sanlo_Chrom1<-mutate(teo_sanlo_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_sanlo_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_sanlo_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

teo_amatlan_Chrom1<-mutate(teo_amatlan_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_amatlan_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_amatlan_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

teo_elrodeo_Chrom1<-mutate(teo_elrodeo_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_elrodeo_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_elrodeo_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

teo_cruc_Chrom1<-mutate(teo_cruc_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_cruc_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_cruc_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

teo_losguajes_Chrom1<-mutate(teo_losguajes_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_losguajes_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=teo_losguajes_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

```

Fixing rounding discrepancies between Bedtools file and Teosinte data so that they can be merged 
```{r}
teo_palmar_Chrom1<- teo_palmar_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
teo_sanlo_Chrom1<- teo_sanlo_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
teo_amatlan_Chrom1<- teo_amatlan_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
teo_elrodeo_Chrom1<- teo_elrodeo_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
teo_cruc_Chrom1<- teo_cruc_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
teo_losguajes_Chrom1<- teo_losguajes_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
All_TEO_Distance_Between_1000BPWindow_and_Gene_CM.txt<- All_TEO_Distance_Between_1000BPWindow_and_Gene_CM.txt %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
```

Merging Bedtools file with Teosinte data
```{r}
Teo_Palmar_Chico_PI_Distance<- full_join(All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,teo_palmar_Chrom1)
Teo_San_Lorenzo_PI_Distance<- full_join(All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,teo_sanlo_Chrom1)
Teo_El_Rodeo_PI_Distance<- full_join(All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,teo_elrodeo_Chrom1)
Teo_Los_Guajes_PI_Distance<- full_join(All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,teo_losguajes_Chrom1)
Teo_Amatlan_De_Casas_PI_Distance<- full_join(All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,teo_amatlan_Chrom1)
Teo_Crucero_Lagunitas_PI_Distance<- full_join(All_TEO_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,teo_cruc_Chrom1)

```

Removing NA and filtering data so that only distance values below .01 are shown
```{r}
Teo_Palmar_Chico_PI_Distance<-drop_na(Teo_Palmar_Chico_PI_Distance) %>% filter(Distance<.01)
Teo_San_Lorenzo_PI_Distance<-drop_na(Teo_San_Lorenzo_PI_Distance) %>% filter(Distance<.01)
Teo_El_Rodeo_PI_Distance<-drop_na(Teo_El_Rodeo_PI_Distance) %>% filter(Distance<.01)
Teo_Los_Guajes_PI_Distance<-drop_na(Teo_Los_Guajes_PI_Distance) %>% filter(Distance<.01)
Teo_Amatlan_De_Casas_PI_Distance<-drop_na(Teo_Amatlan_De_Casas_PI_Distance) %>% filter(Distance<.01)
Teo_Crucero_Lagunitas_PI_Distance<-drop_na(Teo_Crucero_Lagunitas_PI_Distance) %>% filter(Distance<.01)
```

Making a cubic spline for PI vs Distance from Gene for all Teosinte Populations for Chromosome 1
```{r}

smooth.spline(y=Teo_Palmar_Chico_PI_Distance$PI,x=Teo_Palmar_Chico_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="Teo_Palmar_Chico_Chrom_1")

smooth.spline(y=Teo_San_Lorenzo_PI_Distance$PI,x=Teo_San_Lorenzo_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="Teo_San_Lorenzo_Chrom_1")

smooth.spline(y=Teo_El_Rodeo_PI_Distance$PI,x=Teo_El_Rodeo_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="Teo_El_Rodeo_Chrom_1")

smooth.spline(y=Teo_Los_Guajes_PI_Distance$PI,x=Teo_Los_Guajes_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="Teo_Los_Guajes_Chrom_1")

smooth.spline(y=Teo_Crucero_Lagunitas_PI_Distance$PI,x=Teo_Crucero_Lagunitas_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="Teo_Crucero_Lagunitas_Chrom_1")

smooth.spline(y=Teo_Amatlan_De_Casas_PI_Distance$PI,x=Teo_Amatlan_De_Casas_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="Teo_Amatlan_De_Casas_Chrom_1")

```
Putting all PI vs Distance from Gene for TEO on a single plot
```{r}
a<-smooth.spline(y=Teo_Palmar_Chico_PI_Distance$PI,x=Teo_Palmar_Chico_PI_Distance$Distance)
b<-smooth.spline(y=Teo_San_Lorenzo_PI_Distance$PI,x=Teo_San_Lorenzo_PI_Distance$Distance) 
c<-smooth.spline(y=Teo_Amatlan_De_Casas_PI_Distance$PI,x=Teo_Amatlan_De_Casas_PI_Distance$Distance)
d<-smooth.spline(y=Teo_Crucero_Lagunitas_PI_Distance$PI,x=Teo_Crucero_Lagunitas_PI_Distance$Distance)
e<-smooth.spline(y=Teo_Los_Guajes_PI_Distance$PI,x=Teo_Los_Guajes_PI_Distance$Distance)
f<-smooth.spline(y=Teo_El_Rodeo_PI_Distance$PI,x=Teo_El_Rodeo_PI_Distance$Distance)
plot(a, col="blue",lwd=1,type="l",xlim=c(0, .01),ylim=c(0,.02),xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="PI vs Distance for Teosinte for Chromosome 1")
lines(b,cex.lab=2,cex.axis=1.5,lwd=1, type="l",col="red" )
lines(c,cex.lab=2,cex.axis=1.5,lwd=1, type="l",col="green" )
lines(d,cex.lab=2,cex.axis=1.5,lwd=1, type="l",col="orange" )
lines(e,cex.lab=2,cex.axis=1.5,lwd=1, type="l",col="yellow" )
lines(f,cex.lab=2,cex.axis=1.5,lwd=1, type="l",col="purple" )
legend(.002,.01, legend=c("Palmar Chico", "San Lorenzo", "Amatlan de Casas", "Crucero Lagunitas", "Los Guajes", "El Rodeo"),
       col=c("blue", "red", "green","orange","yellow","purple"), lty=1, cex=0.8)

```
Get any possible Window positions from any Land Race population Chrom 1 and rearragning them in the order that bedtools can read 
```{r}
#LRfive_pops_Chrom1<-rbind(lr_palmar_Chrom1,lr_sanlo_Chrom1,lr_amatlan_Chrom1,lr_losguajes_Chrom1,lr_cruc_Chrom1) 
LRWindows <- data.frame(BIN_START=seq(1,307039001,1000),
                 BIN_END=seq(1000,307040000,1000),
                 chrom="chr1")
                 
LRWindows<-LRWindows[c("chrom", "BIN_START", "BIN_END")]

```
Get cm positions for windows in each pop; remove windows with NA (usually because before start of genetic map)
```{r}
LRWindows<-mutate(LRWindows,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=LRWindows$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=LRWindows$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")
```

Cleaning up data, removing columns, renaming certain columns so they can be read by bedtools, converting CM to integers by multiplying 1000000000 and removing decimal places
```{r}
LR_All_POPS_CM_WINDOW_CHROM_1<-Windows %>% select(-BIN_START, -BIN_END,  -rec) %>% mutate(cm_start=cm_start*1000000000, cm_end=cm_end*1000000000) %>% mutate (cm_start=round(cm_start, digits=0), cm_end=round(cm_end, digits=0)) %>% rename( chromStart=cm_start, chromEnd=cm_end)
```


No e in my textfiles...Eliminating scientific notation
```{r}
options(scipen = 999)
```

Make Textfiles for LR Bedtools
```{r}
write.table(LR_All_POPS_CM_WINDOW_CHROM_1, file="LR_All_POPS_CM_WINDOW_CHROM_1.txt",row.names=F,quote=F,sep="\t")
```

Read LR Bedtools distance file
```{r}
read.delim("~/Documents/All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt", header=F, comment.char="#")-> All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt  
```

Renaming Column names for LR Bedtools file
```{r}
All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt<-All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt %>% rename(chromWindow=V1, cm_start=V2, cm_end=V3, chromGene=V4, GeneCM_Start=V5, GeneCM_End=V6, Distance=V7 )
```

Converting integer CM back into CM (Bedtools only reads integers)
```{r}
All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt<-All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt %>% mutate(cm_start=cm_start/1000000000,cm_end=cm_end/1000000000,GeneCM_Start=GeneCM_Start/1000000000,GeneCM_End=GeneCM_End/1000000000, Distance=Distance/1000000000 ) 
```  
Lets get data for our Land Race populations
```{r}
lr_palmar_Chrom1<-filter(allpops_Chrom1,pop=="LR_Palmar_Chico")
lr_sanlo_Chrom1<-filter(allpops_Chrom1,pop=="LR_San_Lorenzo")
lr_amatlan_Chrom1<-filter(allpops_Chrom1,pop=="LR_Amatlan_de_Canas")

lr_cruc_Chrom1<-filter(allpops_Chrom1,pop=="LR_Crucero_Lagunitas")
lr_losguajes_Chrom1<-filter(allpops_Chrom1,pop=="LR_Los_Guajes")
```


Lets get CM positions for our Windows in our Land Race data
```{r}
lr_palmar_Chrom1<-mutate(lr_palmar_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_palmar_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_palmar_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

lr_sanlo_Chrom1<-mutate(lr_sanlo_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_sanlo_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_sanlo_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

lr_amatlan_Chrom1<-mutate(lr_amatlan_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_amatlan_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_amatlan_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")



lr_cruc_Chrom1<-mutate(lr_cruc_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_cruc_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_cruc_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

lr_losguajes_Chrom1<-mutate(lr_losguajes_Chrom1,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_losguajes_Chrom1$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=lr_losguajes_Chrom1$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")

```

Fixing rounding discrepancies between Bedtools file and Land Race data so that they can be merged 
```{r}
lr_palmar_Chrom1<- lr_palmar_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
lr_sanlo_Chrom1<- lr_sanlo_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
lr_amatlan_Chrom1<- lr_amatlan_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))

lr_cruc_Chrom1<- lr_cruc_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
lr_losguajes_Chrom1<- lr_losguajes_Chrom1 %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt<- All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt %>% mutate(cm_start=round(cm_start, digits=8), cm_end=round(cm_end, digits=8))
```

Merging Bedtools file with Land Race data
```{r}
LR_Palmar_Chico_PI_Distance<- full_join(All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,lr_palmar_Chrom1)
LR_San_Lorenzo_PI_Distance<- full_join(All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,lr_sanlo_Chrom1)

LR_Los_Guajes_PI_Distance<- full_join(All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,lr_losguajes_Chrom1)
LR_Amatlan_De_Casas_PI_Distance<- full_join(All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,lr_amatlan_Chrom1)
LR_Crucero_Lagunitas_PI_Distance<- full_join(All_LR_Distance_Between_1000BPWindow_and_Gene_CM_Chrom1.txt,lr_cruc_Chrom1)

```

Removing NA and filtering data so that only distance values below .01 are shown
```{r}
LR_Palmar_Chico_PI_Distance<-drop_na(LR_Palmar_Chico_PI_Distance) %>% filter(Distance<.01)
LR_San_Lorenzo_PI_Distance<-drop_na(LR_San_Lorenzo_PI_Distance) %>% filter(Distance<.01)

LR_Los_Guajes_PI_Distance<-drop_na(LR_Los_Guajes_PI_Distance) %>% filter(Distance<.01)
LR_Amatlan_De_Casas_PI_Distance<-drop_na(LR_Amatlan_De_Casas_PI_Distance) %>% filter(Distance<.01)
LR_Crucero_Lagunitas_PI_Distance<-drop_na(LR_Crucero_Lagunitas_PI_Distance) %>% filter(Distance<.01)
```

Making a cubic spline for PI vs Distance from Gene for all Land Race Populations for Chromosome 1
```{r}

smooth.spline(y=LR_Palmar_Chico_PI_Distance$PI,x=LR_Palmar_Chico_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="LR_Palmar_Chico_Chrom_1")

smooth.spline(y=LR_San_Lorenzo_PI_Distance$PI,x=LR_San_Lorenzo_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="LR_San_Lorenzo_Chrom_1")



smooth.spline(y=LR_Los_Guajes_PI_Distance$PI,x=LR_Los_Guajes_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="LR_Los_Guajes_Chrom_1")

smooth.spline(y=LR_Crucero_Lagunitas_PI_Distance$PI,x=LR_Crucero_Lagunitas_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="LR_Crucero_Lagunitas_Chrom_1")

smooth.spline(y=LR_Amatlan_De_Casas_PI_Distance$PI,x=LR_Amatlan_De_Casas_PI_Distance$Distance) %>%
plot(col="blue",lwd=1,type="l",xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="LR_Amatlan_De_Casas_Chrom_1")

```

Putting all PI vs Distance from Gene on a single plot
```{r}
a<-smooth.spline(y=LR_Palmar_Chico_PI_Distance$PI,x=LR_Palmar_Chico_PI_Distance$Distance)
b<-smooth.spline(y=LR_San_Lorenzo_PI_Distance$PI,x=LR_San_Lorenzo_PI_Distance$Distance) 
c<-smooth.spline(y=LR_Amatlan_De_Casas_PI_Distance$PI,x=LR_Amatlan_De_Casas_PI_Distance$Distance)
d<-smooth.spline(y=LR_Crucero_Lagunitas_PI_Distance$PI,x=LR_Crucero_Lagunitas_PI_Distance$Distance)
e<-smooth.spline(y=LR_Los_Guajes_PI_Distance$PI,x=LR_Los_Guajes_PI_Distance$Distance)

plot(a, col="blue",lwd=1,type="l",xlim=c(0, .01),ylim=c(0,.02),xlab="Distance from Gene in CM",ylab=expression(pi),cex.lab=2,cex.axis=1.5,main="PI vs Distance for Land Race for Chromosome 1")
lines(b,cex.lab=2,cex.axis=1.5,lwd=1, type="l",col="red" )
lines(c,cex.lab=2,cex.axis=1.5,lwd=1, type="l",col="green" )
lines(d,cex.lab=2,cex.axis=1.5,lwd=1, type="l",col="orange" )
lines(e,cex.lab=2,cex.axis=1.5,lwd=1, type="l",col="yellow" )

legend(.002,.02, legend=c("Palmar Chico", "San Lorenzo", "Amatlan de Casas", "Crucero Lagunitas", "Los Guajes"),
       col=c("blue", "red", "green","orange","yellow"), lty=1, cex=0.8)

```

Get any possible Window positions from any population  
```{r}
Windows <- data.frame(BIN_START=seq(1,max(allpops_Chrom1$BIN_START),1000),
                 BIN_END=seq(1000,max(allpops_Chrom1$BIN_START)+1000,1000),
                 chrom="chr1")
                 
Windows<-Windows[c("chrom", "BIN_START", "BIN_END")]

```
Get cm positions for windows in each pop; remove windows with NA (usually because before start of genetic map)
```{r}
Windows<-mutate(Windows,cm_start=approx(x=gen_map$pos,y=gen_map$cm,xout=Windows$BIN_START)$y) %>%
  mutate(cm_end=approx(x=gen_map$pos,y=gen_map$cm,xout=Windows$BIN_END)$y) %>%
  mutate(rec=cm_end-cm_start) %>% filter(rec!="NA")
```

Cleaning up data, removing columns, renaming certain columns so they can be read by bedtools, converting CM to integers by multiplying 1000000000 and removing decimal places
```{r}
All_POPS_CM_WINDOW_CHROM_1<-Windows %>% select(-BIN_START, -BIN_END,  -rec) %>% mutate(cm_start=cm_start*1000000000, cm_end=cm_end*1000000000) %>% mutate (cm_start=round(cm_start, digits=0), cm_end=round(cm_end, digits=0)) %>% rename( chromStart=cm_start, chromEnd=cm_end)
```


